---
title: "Lab: Logistic Regression, LDA, QDA, and KNN"
output: html_notebook
---


###4.6.1 The Stock Market Data

We will begin by examining some numerical and graphical summaries of
the Smarket data, which is part of the ISLR library. This data set consists of
percentage returns for the S&P 500 stock index over 1, 250 days, from the
beginning of 2001 until the end of 2005. For each date, we have recorded
the percentage returns for each of the five previous trading days, Lag1
through Lag5. We have also recorded Volume (the number of shares traded on the previous day, in billions), Today (the percentage return on the date in question) and Direction (whether the market was Up or Down on this
date).

```{r}
library(ISLR)
names(Smarket)
```

```{r}
dim(Smarket )
```

```{r}
summary (Smarket )
```
The cor() function produces a matrix that contains all of the pairwise
correlations among the predictors in a data set. The first command below
gives an error message because the Direction variable is qualitative.

```{r}
cor(Smarket[,-9])
```
As one would expect, the correlations between the lag variables and today’s
returns are close to zero. In other words, there appears to be little
correlation between today’s returns and previous days’ returns. The only
substantial correlation is between Year and Volume. By plotting the data we
see that Volume is increasing over time. In other words, the average number
of shares traded daily increased from 2001 to 2005.

```{r}
attach (Smarket)
plot(Volume )
```
### 4.6.2 Logistic Regression

```{r}

```

