---
title: "Cap 2. Exercises"
output: word_document
---


#### Applied


8. This exercise relates to the College data set, which can be found in
the file **College.csv**. It contains a number of variables for 777 different universities and colleges in the US.

a) Use the **read.csv()** function to read the data into R. Call the
loaded data college. Make sure that you have the directory set
to the correct location for the data.

```{r}
college <- read.csv("https://uclspp.github.io/datasets/data/College.csv")
```


(b) Look at the data using the **fix()** function. You should notice
that the first column is just the name of each university.We don’t
really want R to treat this as data. However, it may be handy to
have these names for later. Try the following commands:

```{r}
rownames(college) = college[,1]
fix (college )
```

You should see that there is now a row.names column with the
name of each university recorded. This means that R has given
each row a name corresponding to the appropriate university. R
will not try to perform calculations on the row names. However,
we still need to eliminate the first column in the data where the
names are stored. Try

```{r}
rownames =college[, 1]
college =college [,-1]
fix (college )
```

Now you should see that the first data column is Private. Note
that another column labeled row.names now appears before the
Private column. However, this is not a data column but rather
the name that R is giving to each row.

(c) i. Use the summary() function to produce a numerical summary
of the variables in the data set.


```{r}
college$Private <- as.factor(college$Private)
summary(college)
```
ii. Use the pairs() function to produce a scatterplot matrix of
the first ten columns or variables of the data. Recall that
you can reference the first ten columns of a matrix A using
A[,1:10].

```{r}
pairs(college[,1:10])
```
iii. Use the plot() function to produce side-by-side boxplots of
Outstate versus Private.


```{r}

plot(college$Private,college$Outstate, main= "Out-of-state tuition", ylab= "Outstate", xlab= "Private")
```

Create a new qualitative variable, called **Elite**, by binning the Top10perc variable. We are going to divide universities into two groups based on whether or not the proportion of students coming from the top 10% of their high school
classes exceeds 50%.
```{r}

Elite =rep ("No",nrow(college ))
Elite [college$Top10perc >50]=" Yes"
Elite =as.factor (Elite)
college =data.frame(college ,Elite)

```

Use the summary() function to see how many elite universities there are.

```{r}
summary(college$Elite)
```
Now use the plot() function to produce
side-by-side boxplots of Outstate versus Elite.

```{r}
plot(college$Elite,college$Outstate, main= "Out-of-state tuition", ylab= "Outstate", xlab= "Elite")
```

v. Use the hist() function to produce some histograms with differing numbers of bins for a few of the quantitative variables. You may find the command par(mfrow=c(2,2)) useful:
it will divide the print window into four regions so that four plots can be made simultaneously. Modifying the arguments
to this function will divide the screen in other ways.


```{r}
par(mfrow=c(2,2))
hist(college$Accept, main = "Accepted", breaks = 12, xlab = "Number of applicants accepted")
hist(college$Enroll, main = "Enroll", breaks = 8, xlab = "Number of new students enrolled")
hist(college$F.Undergrad, main = "F.Undergrad", breaks = 15, xlab = "Number of full-time undergraduates")
hist(college$Outstate, main = "Outstate", breaks = 10, xlab = "Out-of-state tuition")

```
vi. Continue exploring the data, and provide a brief summary
of what you discover.


xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

9. This exercise involves the Auto data set studied in the lab. Make sure
that the missing values have been removed from the data.

```{r}
library(ISLR)
data(Auto)
str(Auto)
```

(a) Which of the predictors are quantitative, and which are qualitative?

Gracias al comando **str()**, podemos ver que todas las variables con excepción de **name** son variables cuantitativas y por ende **name** es un predictor cuantitativo 

(b) What is the range of each quantitative predictor? You can answer
this using the **summary()** function.

```{r}
sapply(Auto[ ,(1:8)], range)
```

(c) What is the mean and standard deviation of each quantitative
predictor?

La media de cada variable predictora esta dada por:

```{r}
sapply(Auto[ ,-9], mean)
```
La desviación estándar de cada variable predictora esta dada por:

```{r}
sapply(Auto[ ,-9], sd)
```


(d) Now remove the 10th through 85th observations. What is the
range, mean, and standard deviation of each predictor in the
subset of the data that remains?

```{r}
# Se ejecuta el subset de los datos

Auto_subset <- subset(Auto[-10:-85,-9])
```

El rango de dado para los datos restantes es:

```{r}

sapply(Auto_subset,range)

```

La media para los datos restantes es:

```{r}

sapply(Auto_subset,mean)

```

La desviación estándar para los datos restantes es:

```{r}

sapply(Auto_subset,sd)

```


(e) Using the full data set, investigate the predictors graphically,
using scatterplots or other tools of your choice. Create some plots
highlighting the relationships among the predictors. Comment
on your findings.

```{r}
pairs(Auto[,-9])
```

```{r}
par(mfrow=c(2,2))
hist(Auto$mpg, main = "MPG", xlab = "miles per gallon")
hist(Auto$horsepower, main = "Horsepower", breaks = 8, xlab = "Engine horsepower")
hist(Auto$weight, main = "Weight", breaks = 15, xlab = "Vehicle weight (lbs.)")
hist(Auto$acceleration, main = "Acceleration", breaks = 10, xlab = "Time to accelerate from 0 to 60 mph (sec.)")

```
xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

(f) Suppose that we wish to predict gas mileage (mpg) on the basis
of the other variables. Do your plots suggest that any of the
other variables might be useful in predicting mpg? Justify your
answer.

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

displacement, horsepower and weight
