---
title: "Cap 2. Exercises"
output: word_document
---


#### Applied


8. This exercise relates to the College data set, which can be found in
the file **College.csv**. It contains a number of variables for 777 different universities and colleges in the US.

a) Use the **read.csv()** function to read the data into R. Call the
loaded data college. Make sure that you have the directory set
to the correct location for the data.

```{r}
college <- read.csv("https://uclspp.github.io/datasets/data/College.csv")
```


(b) Look at the data using the **fix()** function. You should notice
that the first column is just the name of each university.We don’t
really want R to treat this as data. However, it may be handy to
have these names for later. Try the following commands:

```{r}
rownames(college) = college[,1]
fix (college )
```

You should see that there is now a row.names column with the
name of each university recorded. This means that R has given
each row a name corresponding to the appropriate university. R
will not try to perform calculations on the row names. However,
we still need to eliminate the first column in the data where the
names are stored. Try

```{r}
rownames =college[, 1]
college =college [,-1]
fix (college )
```

Now you should see that the first data column is Private. Note
that another column labeled row.names now appears before the
Private column. However, this is not a data column but rather
the name that R is giving to each row.

(c) i. Use the summary() function to produce a numerical summary
of the variables in the data set.


```{r}
college$Private <- as.factor(college$Private)
summary(college)
```
ii. Use the pairs() function to produce a scatterplot matrix of
the first ten columns or variables of the data. Recall that
you can reference the first ten columns of a matrix A using
A[,1:10].

```{r}
pairs(college[,1:10])
```
iii. Use the plot() function to produce side-by-side boxplots of
Outstate versus Private.


```{r}

plot(college$Private,college$Outstate, main= "Out-of-state tuition", ylab= "Outstate", xlab= "Private")
```

Create a new qualitative variable, called **Elite**, by binning the Top10perc variable. We are going to divide universities into two groups based on whether or not the proportion of students coming from the top 10% of their high school
classes exceeds 50%.
```{r}

Elite =rep ("No",nrow(college ))
Elite [college$Top10perc >50]=" Yes"
Elite =as.factor (Elite)
college =data.frame(college ,Elite)

```

Use the summary() function to see how many elite universities there are.

```{r}
summary(college$Elite)
```
Now use the plot() function to produce
side-by-side boxplots of Outstate versus Elite.

```{r}
plot(college$Elite,college$Outstate, main= "Out-of-state tuition", ylab= "Outstate", xlab= "Elite")
```

v. Use the hist() function to produce some histograms with differing numbers of bins for a few of the quantitative variables. You may find the command par(mfrow=c(2,2)) useful:
it will divide the print window into four regions so that four plots can be made simultaneously. Modifying the arguments
to this function will divide the screen in other ways.


```{r}
par(mfrow=c(2,2))
hist(college$Accept, main = "Accepted", breaks = 12, xlab = "Number of applicants accepted")
hist(college$Enroll, main = "Enroll", breaks = 8, xlab = "Number of new students enrolled")
hist(college$F.Undergrad, main = "F.Undergrad", breaks = 15, xlab = "Number of full-time undergraduates")
hist(college$Outstate, main = "Outstate", breaks = 25, xlab = "Out-of-state tuition")

```
vi. Continue exploring the data, and provide a brief summary
of what you discover.


xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

```{r}

```

