---
output: word_document
---


6. We continue to consider the use of a logistic regression model to
predict the probability of default using income and balance on the
Default data set. In particular, we will now compute estimates for
the standard errors of the income and balance logistic regression coefficients
in two different ways: (1) using the bootstrap, and (2) using
the standard formula for computing the standard errors in the glm()
function. Do not forget to set a random seed before beginning your
analysis.



```{r}
library("ISLR")
data(Default)
attach(Default)
```


a) Using the **summary()** and **glm()** functions, determine the estimated
standard errors for the coefficients associated with **income**
and **balance** in a multiple logistic regression model that uses
both predictors.


```{r}

glm.fit = glm(default ~ income + balance, family=binomial)
summary(glm.fit)

```
Se puede ver con claridad que tanto **income** como **balance** son variables predictoras significativas para este modelo pues p-value < .05; sin embargo tanto la **desviación residual** como el **AIC**, son muy grandes, lo cual es un indicativo que el modelo entrenado no es el más el adecuado.


b) Write a function, **boot.fn()**, that takes as input the Default data
set as well as an index of the observations, and that outputs
the coefficient estimates for income and balance in the multiple
logistic regression model.



```{r}

##Se establece una semill para que los resultados siempre sean replicables.

set.seed(13) 
boot.fn <- function(data, index) {
    fit <- glm(default ~ income + balance, data = data, family = "binomial", subset = index)
    return (coef(fit))
}
```

(c) Use the boot() function together with your boot.fn() function to
estimate the standard errors of the logistic regression coefficients
for income and balance.

```{r}
set.seed(13)
library(boot)
boot(Default, boot.fn, 1000)
```

Los estimados de los errores estandar generados por el boostrap son:

 + $\hat{\beta_0} = 4.11e-01$
 + $\hat{\beta_1} = 4.57e-06$
 + $\hat{\beta_2} = 2.16e-04$


(d) Comment on the estimated standard errors obtained using the
**glm()** function and using your bootstrap function.

Al comparar los resultados de los errores estándar estimados 
para los puntos (c) y (d),vemos que son muy cercanos entre sí, 
por lo cual se puede decir que el modelo boostrap es eficiente. 

La cercania entre estos valores es cada vez más notoría al incrementar
el numero de observaciones utilizadas en el boostrap como se puede ver
a continuación.


```{r}
## Boostrap con 100 datos

set.seed(13)
library(boot)
boot(Default, boot.fn, 100)
```

```{r}
## Boostrap con 5000 datos
set.seed(13)
library(boot)
boot(Default, boot.fn, 5000)
```
