---
title: "Cap 8. Exercises"
output: word_document
---



8. This question involves the use of simple linear regression on the Auto
data set.

```{r}
library("ISLR")
data(Auto)
attach(Auto)
```

(a) Use the lm() function to perform a simple linear regression with
mpg as the response and horsepower as the predictor. Use the
summary() function to print the results. Comment on the output.
For example:

```{r}
lm.fit <- lm(mpg ~ horsepower)
summary(lm.fit)
```

i. Is there a relationship between the predictor and the response?

Sí, existe una relación entre **horsepower** y *mpg*, puesto que p-value < 0.05, por lo tanto se rechaza **Ho**, estando esta relación dada por la ecuacion:

$$ mpg = 39.93 -0.158*horsepower + \epsilon $$

ii. How strong is the relationship between the predictor and
the response?

```{r}
### Media de la variable respuesta

media_y <- mean(mpg)
media_y
```
```{r}
### Media de la variable respuesta

porcentaje_error <-  4.906/media_y
porcentaje_error
```


Para los datos de **Auto**, **RSE** es **4.906**, mientras que la media para **mpg** es **23.45**, indicando un percentage de error del **21%**. Mientras que el porcentaje de la variabilidad en la respuesta esta dado por **R^2 = 0.6059 **, es decir que **horsepower** explica el **61%** de la varianza de **mpg**.

iii. Is the relationship between the predictor and the response
positive or negative?

La relacion entre **mpg** y **horsepower** es negativa, es decir que por cada caballo de fuerza adicional, la disminución promedio de las millas por galon que pude realizar el vehiculo  disminuye **0.158**

iv. What is the predicted mpg associated with a horsepower of
98? What are the associated 95% confidence and prediction
intervals?

El intervalo de confianza para **horsepower  = 98** esta dado por:

```{r}
predict(lm.fit, data.frame(horsepower = 98), interval = "confidence")
```
El intervalo de predicción para **horsepower  = 98** esta dado por:

```{r}
predict(lm.fit, data.frame(horsepower = 98), interval = "prediction")
```


(b) Plot the response and the predictor. Use the abline() function
to display the least squares regression line.

```{r}
plot(horsepower,mpg, main = "mpg vs. horsepower", xlab="horsepower", ylab="mpg")
abline(lm.fit, col="red")
```


(c) Use the plot() function to produce diagnostic plots of the least
squares regression fit. Comment on any problems you see with
the fit.



```{r}
par(mfrow = c(2, 2))
plot(lm.fit)
```
